\chapter{Accelerator facilities and experimental apparatus}
\minitoc

\InitialCharacter{T}he Large Hadron Collider (\texttt{LHC}) is a hadron accelerator with a circumference of 26.7\,$\mathrm{km}$ designed to operate separately with proton and lead beams with energies of up to 7 and 7\,$Z$\,\TeV, respectively. It features four experimental insertions: two aiming at instantaneous luminosity of at least $10^{34}$\,$\mathrm{cm}^{-2}\mathrm{s}^{-1}$, 
and the rest dedicated to ``medium'' ($\sim$\,$10^{32}$\,$\mathrm{cm}^{-2}\mathrm{s}^{-1}$) and ``low'' ($\sim$\,$10^{29}$\,$\mathrm{cm}^{-2}\mathrm{s}^{-1}$) interaction rates using pp collisions. 
The \texttt{CERN} heavy ion injectors and \texttt{LHC} have demonstrated the feasibility of proton-lead as well as xenon-xenon collisions.
Bunches can be injected into the \texttt{LHC} in every 10th of the 35\,640 RF buckets, a spacing conventionally referred to as ``25\,$\mathrm{ns}$,'' although 
other spacings exist and can be any multiple of 25\,$\mathrm{ns}$. The minimum spacing between heavy ion bunches, as dictated from the injectors, is nominally 100\,$\mathrm{ns}$. 
\texttt{LHC} has  very  tight  tolerances  on  nearly  all  beam  parameters,  meaning their  precise  measurement  is  crucial   for   controlling   and   understanding   the  apparatus. 
With at least two   orders   of   magnitude   higher   stored   beam   energy   than   previous   colliders  machine  protection is also imperative.

The Compact Muon Solenoid (\texttt{CMS}) detector is one of the two general-purpose experiments operating at \texttt{LHC}. 
Its central feature is a superconducting solenoid of 6\,$\mathrm{m}$ internal diameter.  
Within the solenoid volume are a silicon pixel and strip tracker, a lead tungstate crystal electromagnetic calorimeter, and a brass and scintillator hadron calorimeter, 
each composed of a barrel and two endcap sections. Muons are detected in gas-ionization chambers embedded in the steel flux-return yoke outside the solenoid. 
The forward hadron calorimeter uses steel as an absorber and quartz fibers as the sensitive material, and extend the coverage in the range $3.0 <\lvert \eta \rvert < 5.2$.

\clearpage

%\input{apparatus/introduction.tex}

\input{apparatus/lhc.tex}
\input{apparatus/cms.tex}